A generalization of Plackett-Luce likelihoods to incorporate non-independence of competitors

### 2023-01-06 inst/plackett_luce_monster.Rmd
rewording

---
title: "plackett_luce_monster"
output: html_document
date: '2022-05-16'
---

@@

%

There seem to be a few distinct statistical models for nonindependence:

>>>>

---
title: "A generalization of Plackett-Luce likelihoods to incorporate non-independence of competitors"
output: html_document
date: '2022-05-16'
---

@@

Here I modify standard Plackett-Luce likelihood functions to include
an element of non-independence among the competitors.  There seem to
be a few distinct statistical models for nonindependence:
